\documentclass{article}

\begin{document}

\section{3 Idiots}
	
I'm an IITian myself and hence, needless to say, was looking forward to this movie as it is based on the life in IITs. I went with my family and watched the first-day-first-show and was I pleased ? In one sentence - The best Bollywood movie ever ! If you are into movies, then this one is not to be missed unless you are the 4th idiot. I cried, I laughed and I enjoyed every moment of the 3 hours that I spent watching this gem. The songs that seemed mediocre before watching the movie, feel like perfect for the movie. They are so ideal for the situations that I just loved them.

As you can understand, they could not bring the name of any IIT into the movie to avoid disputes. But trust me, whatever they have shown about the life in IITs, it's all true. Right from suicides, cold-hearted Professors to lack of encouragement and support for talents who can really bring serious change in this world. The movie successfully depicts how once inside, your life is only about meaningless grades, go get into the race before it's too late.

Take my free advice and avoid any reviews or words from people who have already seen the movie. Don't let anyone spoil any scene from the movie. Rush to the nearest theater and experience the phenomenon for yourself. You'll bless me for this advice !

\section{Sholay}
	

Can't find a single flaw in the movie. Probably one of the best ever made in Hindi. The camera work is flawless and grips you. The acting is outstanding. The music is memorable. One of the movies you remember for life and maybe in afterlife . 




\end{document}
